### 2016-03-03 ch02-qlogms/excitation-design.tex
Fix guidelines

\paragraph{System and noise model}
%TODO: move this paragraph forward (before Fi matrix)
  In the remainder of this chapter, an \gls{OE} setting is used.
  Denote
    $U  \left(\omega\right)$ as the excitation signal,
    $\true{Y}\left(\omega\right)$ the exact, unperturbed system output,
    $E  \left(\omega\right)$ for the output noise source,
    $Y  \left(\omega\right) = \true{Y}\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal as shown in \figref{fig:excitation:OE}.
    The output noise is assumed to be zero-mean and white with a standard deviation of $\sigma_e$ in the time domain or $\sigma_E$ in the frequency domain.

@@

@@

  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies well within the `bulk' of the frequency grid with finite support, i.e. $\RightOpenInterval{\frac{2\pi \Delta f}{\alpha - 1}, +\infty}$.
  In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when
  \begin{equation} 
    \frac{2 \pi \Delta f}{\alpha -1} \leq \left( 1 - \damping \right) \wn
    \text{.}
    \label{eq:excitation:systemInBulk:generic}
  \end{equation}
  For more reliable results, however, it is adviced to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
  In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.

@@

>>>>

@@

  Denote
    $U  \left(\omega\right)$ as the excitation signal,
    $\true{Y}\left(\omega\right)$ the exact, unperturbed system output,
    $E  \left(\omega\right)$ for the output noise source,
    $Y  \left(\omega\right) = \true{Y}\left( \omega \right) + E\left( \omega \right)$ depicts the measured output signal as shown in \figref{fig:excitation:OE}.
    The output noise is assumed to be zero-mean and white with a standard deviation of $\sigma_e$ in the time domain or $\sigma_E$ in the frequency domain.

@@

  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies well within the `bulk' of the frequency grid with finite support, i.e. $\RightOpenInterval{\frac{2\pi \Delta f}{\alpha - 1}, +\infty}$.
  In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when
  \begin{equation} 
    \frac{2 \pi \Delta f}{\alpha -1} \leq \left( 1 - \damping \right) \wn
    \text{.}
    \label{eq:excitation:systemInBulk:generic}
  \end{equation}
  %TODO: turn this into a guideline?
  For more reliable results, however, it is advisable to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
  In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.

@@

\TODO{move this guideline somewhere else}
\begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of many sharp resonance peaks over a wide frequency band of interest with a constant quality.
\end{guideline}
